Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-05-09 paper/main.tex
LaTex formatting madness; wrote statistical analysis section

\begin{abstract}
% < 170 words
% new analysis of existing data
% of interest to a broad section of our audience
% highlighting innovative examples of data reuse
% may be used to present compelling new findings & conclusions derived from published data.
Intro: PPA as classic example for an visual area
Methods: fMRI data, studyforrest data set, general linear model
Results: significant clusters in PPA, RSC, individual results in x of 15 subjects
Conclusions: PPA nicht exclusively
\end{abstract}
\todo[inline]{Vorgabe: Intro + Discussion = main text ~ 3,000 words; einige offene Dinge sind folgend in Kommentaren und nicht als ToDo gemarkt}
\todo[inline]{include figure providing schematic overview of the study and assay(s) design -> is overkill: Steht in den entsprechenden Veröffentlichungen \& Paradigma ist mit "Film ab" wenig kompliziert}
\todo[inline]{our system cannot accept BibTeX bibliography files; authors who wish to use BibTeX to prepare their references should therefore copy the reference list from the .bbl file that BibTeX generates and paste it into the main manuscript .tex file (and delete the associated  \textbackslash{}bibliography and \textbackslash{}bibliographystyle commands); yeah, whatever. Arbeite erstmal mit der references.bib; und habe oben usepackage{natbib}' eingefügt}
\section{Introduction}
Cognitive neuroscientists use brain imaging methods like blood oxygenation level-dependent functional magnetic resonance imaging (BOLD fMRI) to map perceptual and cognitive brain processes (e.g. viewing of landscapes, \citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to functional brain areas or networks.
Brain mapping studies have traditionally employed small sets of carefully chosen, simplified stimuli to strictly control experimental conditions and facilitate functional isolation of brain areas.
The disadvantage is that a limited number of simplified stimuli does not resemble our real-life experience and lacks external \citep{westfall2016fixing} as well as ecological validity \citep{hasson2004intersubject}.
Additionally, brain mapping studies have traditionally averaged / usually average results across at least 10-15 subjects to improve the signal-to-noise-ratio (SNR).
The disadvantage here is that the averaging approach does not characterize brain functions at an individual level, a prerequisite for the application of brain imaging methods in individual diagnostics (cf. \citep{dubois2016building})
\todo[inline]{Retrosplenial Cortex kommt in Einleitung (momentan) nicht vor; wird aufgrund der Ergebnisse AV und AO in Discussion diskutiert werden; ist in den geplanten Abbildungen / Slices aber nicht zu sehen}
A classic example of a functional, higher-level visual area is the ``parahippocampal place area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
The PPA is located in the posterior parahippocampal gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus, both being part of the ventral visual stream \citep{mishkin1982contribution, goodale1992separate}.
Increased hemodynamic activity in the PPA correlates with the perception of static pictures of landscapes or landmarks compared to pictures of tools or faces.
According to the spatial layout hypothesis, the PPA is involved in processing the surface geometry of a visual stimulus and possibly in identifying scenes based on their spatial layout \citep{epstein2010reliable}.
% Überblick
At a group avergae level, results generalize to mental imagination of landscapes \citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO blocks \citep{wolbers2011modality}.
One study that used spoken, place-related sentences showed significantly decreased activation in the left and no modulation in the right-hemispheric PPA \citep{aziz2008modulation}.
\todo[inline]{Egal, was ich folgend in der Überblick \& später im Detail bzgl. Aziz (2008) schreibe, es wird wahrscheinlich nicht korrekt sein; so wie ich es verstanden habe, hat Aziz den Unterschied zwischen PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related Sentences; s. dortige Fig 3; im Grunde kommt da aber überall nur uneinheitliche Grütze raus => bitte gemeinsam im Gespräch checken}

% Im Einzelnen
In the study conducted by \citep{ocraven2000mental} participants viewed alternating blocks of pictures showing famous faces and familiar places during an initial experimental paradigm.
In a subsequent paradigm, participants were instructed to ``form a vivid mental image'' of the previously viewed pictures.
The PPA showed increased activation during imagination of places compared to faces but the imagination tasks showed a smaller activation level compared to the perceptual task.

% Folgend: Wolbers. Er hat noch ne Connectivitäts-Analyse mit dem Occipital Cortex gemacht. Zum visuellen Paradigma ist da dann keine keine Connectivity im Vergleich zum visuellen Paradigma. Seine Interpretation: Es kann keine mental imagery sein:
% "The scene-related increase in coupling with the PPA was significantly stronger in multiple clusters in occipital cortex under visual than haptic stimulation (Figure 2B; Table S2)"
In the block design study conducted by \citep{wolbers2011modality} the PPA of sighted participants showed increased activation during a delayed matching-to-sample task of haptically explored scenes constructed from LEGO bricks compared to haptically explored abstract geometric objects.

% Aziz hat auf eine zweite Mail geantwortet: Sie modelt die HRF über den jeweils gesamten Satz von ca. 2.8 Sekunden.
% wie oben im Kommentar erwähnt: Ihre Method Section halte ich für etwas strange.Ich zeige dir ganz am Ende mal ihr Paper; hab die entsprechenden Stellen annotiert. Sonst wird hier im Detail Mist erzählt
To our knowledge only one study by \citep{aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences.
Sentences described generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting pool'') or faces  (e.g. ``Marylin Monroe has a large square jaw'').
\todo[inline]{\dots and compared those to a control condition of object-related sentences}
Participants were instructed to press a button whenever the sentence described an inaccurate or improbable fact.
Surprisingly, activation in the left, but not right, PPA was significantly reduced when participants listened to place-related sentences compared to listening to face-related sentences.
Moreover, this effect was only observed in sentences involving famous places.

\todo[inline]{Review von Aminoff (2013) kommt nur kurz als "competing hypothesis"; muss man dann natürlich in der Discussion diskutieren; was aber ggf. gar nicht notwendig ist, weil's darum gar bei uns gar nicht geht}
In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information.
This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general (see \citep{aminoff2006parahippocampal} for a review).
Independent(ly) from competing theories (s. \citep{aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.
\todo[inline]{aber Huth, 2016, implizit; diskutiert PPA als solches jedoch gar nicht -> noch mal checken}
\todo[inline]{Coolnessfaktor von naturalistic stimuli ist beinahe komplett raus; Data-driven vs. theory-driven analyses ist komplett raus -> vgl. Speech-Anno-Paper; jedoch in Discussion bringen (s. dort); ggf. erwähnen, dass möglichst ähnliche und nicht fancy analysis gewählt wurde, um Replizierung der Ergebnisse, aber mit naturalistic stimuli zu gewährleisten.}
All revied studies used a just a small set of carefully designed, simplified stimuli to strictly control experimental conditions.
They further relied on / implemented explicit judgment-based tasks to keep participants alert and paying attention.
Thus, they cannot / could answer the question how the PPA might behave under life-like conditions.
Naturalistic stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimuli that better resemble our experience of a continuous dynamic environment.
Two early studies using naturalistic stimuli suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [+++ der Schlusssatz ist aus hasson und bartels plagiiert \citep{bartels2004mapping, hasson2004intersubject}+++]

% Bartels (2004) und Hasson (2004)
\citep{bartels2004mapping} manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}.
Employing a general linear model to model hemodynamic activity, these time points correlated with increased activity in the ``fusiform face area'' \citep{kanwisher1997ffa} and ``extrastriate body area'' \citep{downing2001bodyarea} respectively.
Employing a reverse intersubject correlation, \citep{hasson2004intersubject} used a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}.
fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) corresponding movie frames.
Results revealed that corresponding movie frames depicted indoor and outdoor scenes including buildings and open fields.
Nevertheless, no study investigated how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.

@@

% Präteritum oder Präsens? Ist momentan gemischt; find's ok so.
% N=14 is inner join of AV & AO
\todo[inline]{The next paragraphs contain a bunch of methods already; reduce this to talk about the general approach:
    a) annotation of events,
    b) investigation of model quality,
    c) cross-analysis of datasets.
    d) Possibly cite https://psyarxiv.com/sdbqv/
    and declare that this study is a concrete realization of that promise
}
In this study, we analyze data of three publicly available datasets from the same set of 14 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}).
We exploratorily investigate how the parahippocampal gyrus [or more general ``human brain''?] responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and its audio-description (i.e. the audio-only variant) of the same length \citep{hanke2014audiomovie}.
We compare these results to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}.

Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
We annotated events in the otherwise unknown temporal structure of both stimuli.
In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut.
In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.

In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
% Practical reasons = Es war viel einfacher nouns der audio-description als Frameinhalt des Films zu annotieren
For practical reasons, and encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like stimulus free from any task to localize a ``visual area'' in individual study participants.

\section{Methods}
\todo[inline]{Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below)}
\todo[inline]{statement how often datasets have been analyzed be independent groups -> Frage: ist die Liste auf psychoinformatics.de ist aktuell/erschöpfend? Ist dann schnell eingebaut}
We used data from three publicly available datsets as part of the studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already been used by other research groups for independent research questions before
We used fMRI data from 14 subjects who took part in three different studies. Namely, the same subjects were
a) listening to the audio-description (AO study) \citep{hanke2014audiomovie}) of the movie ``Forrest Gump'', a dataset already used by [XY].
b) watching the actual audio-visual movie (AV study) \citep{hanke2016simultaneous}, a dataset already used by [XY].
c) participating in a dedicated block-wise visual localizer (LOC study) \citep{sengupta2016extension}, a dataset aready used by [XY].
An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in the corresponding publications  \citep{hanke2014audiomovie, hanke2016simultaneous, sengupta2016extension}.
Following is a brief summary of most important aspects.
\todo[inline]{um Sengupta ergänzen}

\subsection{Participants}
\todo[inline]{ich habe von den aligned data eine Intersection von 14 VPN aus AO und AV; in der Speech-Anno-Validation (7T only) habe ich 19 VPN; es fehlt jeweils VP10; demographische Daten bzgl. (Durchschnitts)Alter und Geschlecht ist folglich falsch}
In the AO study, 19 participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest Gump'' \citep{ForrestGumpMovie} as an additional audio track for visually impaired listeners on Swiss public television.
In the AV study, the same 14 participants [+++VP 10 wurde nicht genutzt+++] (21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track \citep{ForrestGumpDVD}.

\todo[inline]{Daten zu Sengupta einarbeiten}
In the LOC study\dots

All participants reported to have normal hearing, normal or corrected-to-normal vision, and no known history of neurological disorders.
% mit LOC study updaten
In both studies, participants received monetary compensation and gave written informed consent for their participation and for public sharing of all obtained data in anonymized form. The studies had prior approval by the Ethics Committee of Otto-von-Guericke University of Magdeburg, Germany.

\subsection{Stimuli}
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned audio-description (i.e. the audio-only variant of the movie) that was broadcast as an additional audio track for visually impaired listeners on Swiss public televinsion \citep{ForrestGumpGermanAD}.
The plot of the movie is already carried by an off-screen voice of the main character Forrest Gump.
In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content.
The audio-description was temporally aligned to the audio track of the German DVD release. A few scenes less relevant to the major plot were removed to create the ``research cut'' lasting $\approx$2h \citep{hanke2014audiomovie,hanke2016simultaneous}.
Both stimuli were further processed (filtering, volume adjustments) to improve audibility during MRI scanning.
Finally, each stimulus was split into eight segments of approximately 15 minutes.
Except for the first movie segment, each segment started with a snippet of at least six seconds immediately preceding the movie scene boundary used to split the segments (s. Figure 3a in \citep{hanke2014audiomovie}.
\todo[inline]{Sengupta: Stimuli}
% LOC study?

\subsection{Stimulus Annotation}
% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
\todo[inline]{WARUM WAS WIE annotiert wurde}
\todo[inline]{aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen \& anpassen, um Statistiken und runcommand-file zu erstellen}
We extended a publicly available annotation of speech \citep{haeusler2020speechanno} by manually annotating the audio-description's narrator:
Two persons performed a categorization of nouns embedded in sentences spoken by the narrator to describe the movie's missing visual content.
\todo[inline]{Warum wurden diese Kategorien so gewählt}
\todo[inline]{Maybe just cite the table}
The nouns were categorized by the clue they provide about the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
See Table \ref{tab:descr-nouns} for a complete overview of all cateogries, [+++rules, counts, examples].

@@

% Tabelle der Descriptive Nouns;
\todo[inline]{wenn decriptive-statistics-anno.py angepasst und Datei mit newcommands geschrieben, Schrägstrich vor die jeweiligen Platzhalter setzen, damit commands daraus werden; Caption hübsch machen}

@@

    \caption{Narrator's descriptive nouns. All categories sorted alphapetically. Examples are given in English. Tabelle enthält bei den Counts Platzhalter für die commands, die ins .tex-file geschrieben werden.}

@@

\subsection{Procedure}
In both studies, participants filled out a questionnaire on their basic demographic information and familiarity with the audio-description or the movie.
Participants were instructed to inhibit physical movements except for eye-movements, and otherwise to simply "enjoy the audiobook" or "enjoy the movie" respectively.
Audio-description and movie segments were presented in chronological order with four segments in two fMRI sessions respectively.
Between sessions, participants left the scanner for a break with a flexible duration. Structural images were obtained during the first study on a day different from the fMRI session.
% At the start (of each?) recording session, participants listened to music from the movie's closing credits segment to individually determine optimal stimulus volume.
% Participants were instructed to ``maximize the volume of the stimulus without it becoming unpleasantly loud or causing acoustic distortions by overdriving the loudspeaker hardware''.

\subsection{Stimulation setup}
\todo[inline]{irrelevantes kürzen}
In both studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
In the AO study, visual instructions were presented on a rear-projection screen inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.).
During the functional scans, the projector presented a medium gray screen with the primary purpose to illuminate a participant's visual field in order to prevent premature fatigue.
[The screen contained a solid black ``fixation'' dot that faded in and out at the beginning and end of a movie segment.]

In the AV study, visual instructions and stimuli were presented on a rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with EXT-DVI-FM1000).
The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p} resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with \unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$ 21.2]{cm}, corresponding to \unit[23.75 $\times$ 13.5] or \unit[23.75 $times$ 10.25]{cm} when considering only the movie content and excluding the horizontal gray bars.

@@

sex\_u & person(s) of unknown sex & \aoSexuAll & \aoSexuI & \aoSexuII & \aoSexuIII & \aoSexuIV & \aoSexuV & \aoSexuVI & \aoSexuVII & \aoSexuVIII \tabularnewline

>>>>

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.
Intro: PPA as classic example for an visual area; Methods: fMRI data
studyforrest data set, general linear model; Results: significant clusters in
PPA, RSC, individual results in x of 15 subjects; Conclusions: PPA nicht
exclusively \end{abstract}

\todo[inline]{Vorgabe: Intro + Discussion = main text ca. 3,000 words; einige
offene einige Dinge sind folgend in Kommentaren und nicht als ToDo gemarkt}

\todo[inline]{include figure providing schematic overview of the study and assay
design -> is overkill: Steht in den entsprechenden Veröffentlichungen \&
Paradigma ist mit "Film ab" wenig kompliziert}

\todo[inline]{our system cannot accept BibTeX bibliography files; authors who
    wish to use BibTeX to prepare their references should therefore copy the
    refernce list from the .bbl file that BibTeX generates and paste it into the
    main manuscript .tex file (and delete the associated
    \textbackslash{}bibliography and \textbackslash{}bibliographystyle
commands)}

\todo[inline]{Ich arbeite erstmal wie gehabt mit der references.bib
    und habe oben usepackage{natbib}' eingefügt}

\section{Introduction} Cognitive neuroscientists use brain imaging methods like
blood oxygenation level-dependent functional magnetic resonance imaging (BOLD
fMRI) to map perceptual and cognitive brain processes (e.g. viewing of
landscapes, \citep{epstein1998ppa}; or theory of mind
\citep{spunt2014validating}) to functional brain areas or networks. Brain
mapping studies have traditionally employed small sets of carefully chosen,
simplified stimuli to strictly control experimental conditions and facilitate
functional isolation of brain areas. The disadvantage is that a limited number
of simplified stimuli does not resemble our real-life experience and lacks
external validity \citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}. Additionally, brain mapping studies usually
average results across at least 10-15 subjects to improve the
signal-to-noise-ratio (SNR). The disadvantage here is that the averaging
approach does not characterize brain functions at an individual level, a
prerequisite for the application of brain imaging methods in individual
diagnostics (cf. \citep{dubois2016building})

\todo[inline]{Retrosplenial Cortex kommt in Einleitung bisher  nicht vor; wird
aufgrund der Ergebnisse in AV und AO in Discussion diskutiert werden; cluster
sind in den Abbildungen nicht zu sehen; kommen aber in (den Tabellen) der
Results Section }

% Was ist PPA?
A classic example of a functional, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}. The PPA is located in the posterior parahippocampal
gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus,
both being part of the ventral visual stream \citep{mishkin1982contribution,
goodale1992separate}. Increased hemodynamic activity in the PPA correlates with
the perception of static pictures of landscapes or landmarks compared to
pictures of tools or faces.  According to the spatial layout hypothesis, the PPA
is involved in processing the surface geometry of a visual stimulus and possibly
in identifying scenes based on their spatial layout \citep{epstein2010reliable}.

% Literature Review PPA: Einleitung
At a group avergae level, results generalize to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}. One study that used spoken, place-related
sentences showed significantly decreased activation in the left and no
modulation in the right-hemispheric PPA \citep{aziz2008modulation}.

% Studien im Einzelnen: O'Craven: Mental imagery
In the study conducted by \citep{ocraven2000mental} participants viewed
alternating blocks of pictures showing famous faces and familiar places during
an initial experimental paradigm. In a subsequent paradigm, participants were
instructed to ``form a vivid mental image'' of the previously viewed pictures.
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.

% Wolbers: haptic exploration
In the block design study conducted by \citep{wolbers2011modality} the PPA of
sighted participants showed increased activation during a delayed
matching-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to haptically explored abstract geometric objects.

\todo[inline]{Er hat noch eine Connectivitäts-Analyse mit dem Occipital Cortex
gemacht. Im Vergleich zum visuellen Paradigma ist im haptischen Paradigma keine
Connectivität. Interpretation: Es kann keine mental imagery sein}

\todo[inline]{"The scene-related increase in coupling with the PPA was
significantly stronger in multiple clusters in occipital cortex under visual
than haptic stimulation (Figure 2B; Table S2)"}

% Aziz (2008): place related sentences
\todo[inline]{Aziz hat auf eine zweite Mail geantwortet: Sie modelt die HRF über
den jeweils gesamten Satz von ca. 2.8 Sekunden}

\todo[inline]{Ihre Method Section ist strange und es bei ihr überall eh nur
    uneinheitliche Grütze heraus; Ich blicke nicht durch; was folgend kommt,
    wird nicht vollständig korrekt sein. So wie ich es verstanden habe, hat sie
    den Unterschied zwischen PPA und FFA angeguckt, aber diesen Unterschied im
Kontrast zu object-related Sentences (dortige Fig 3; lass uns kurz im Gespräch
drübergucken, ich habe die relvanten Abschnitte in der PDF markiert)}

To our knowledge only one study by \citep{aziz2008modulation} correlated
hemodynamic activity of the PPA with spoken sentences.  Sentences described
generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting
pool''), faces  (e.g. ``Marylin Monroe has a large square jaw''), or objects
(e.g. ``The television has a long antenna')'. Participants were instructed to
press a button whenever the sentence described an inaccurate or improbable fact.
Surprisingly, activation in the left, but not right, PPA was significantly
reduced when participants listened to place-related sentences compared to
listening to face-related sentences. Moreover, this effect was only observed in
sentences involving famous places.

\todo[inline]{Review von Aminoff (2013) kommt nur kurz als "competing hypothesis"; muss man dann natürlich in der Discussion diskutieren; was aber ggf. gar nicht notwendig ist, weil's darum gar bei uns gar nicht geht}

% Summary if literature review
In summary, studies suggest that the PPA does not exclusively respond to
visual(ly) spatial information. This is consistent with a competing hypotheses
stating the PPA does not process the spatial layout of a scene specifically but
contextual associations in general (\citep{aminoff2006parahippocampal,
aminoff2013role}). It is still uncertain if auditory stimuli lead to inhibitory
or excitatory responses, or no change at all in the PPA.

\todo[inline]{aber Huth (2016) implizit; diskutiert PPA also solches jedoch
nicht und macht voxel-wise encoding, was - glaube ich - über
excitation/inhibition nichts aussagt -> Paper checken}

% Shortcomings of previous studies; lack of research
All revied studies used a just a small set of carefully designed, simplified
stimuli to strictly control experimental conditions. They further relied on
explicit judgment-based tasks to ensured that participants payed attention to
the stimuli. This raises the question how the PPA behaves under life-like conditions.

\todo[inline]{Data-driven vs. model-driven analyses ist komplett raus; in
Discussion bringen (vgl. Speech-Anno-Paper}

% Why naturalistic stimuli
Naturalistic stimuli like movies \citep{hasson2008neurocinematics,
sonkusare2019naturalistic} or narratives \citep{honey2012not,
lerner2011topographic, silbert2014coupled} offer complex, continuous stimuli
that better resemble our experience of a our dynamic environment.

% Literature review naturalistic stimuli: Einleitung
Two early studies using naturalistic stimuli suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [+++ der Schlusssatz ist aus hasson und bartels plagiiert \citep{bartels2004mapping, hasson2004intersubject}+++]

% Bartels (2004): Film + GLM (jedoch ohne PPA) und Hasson (2004)
\citep{bartels2004mapping} manually annotated time points that depict faces and
human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
[+++Ref+++].
Employing a general linear model (GLM) to model hemodynamic activity, these time
points correlated with increased activity in the ``fusiform face area''
\citep{kanwisher1997ffa} and ``extrastriate body area''
\citep{downing2001bodyarea} respectively.

% Hasson (2004): Film + (reverse) ISC
Employing a reverse intersubject correlation, \citep{hasson2004intersubject}
used a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}
[+++Ref+++]. fMRI
brain volumes showing the highest hemodynamic activity in the PPA [across (five)
participants] were matched to the temporally corresponding movie frames.
Results revealed that corresponding movie frames depicted indoor and outdoor
scenes including buildings and open fields.

% Summary naturalistic stimuli
Nevertheless, no study investigated how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.
\todo[inline]{Huth (2016) checken}

\todo[inline]{The next paragraphs contain a bunch of methods already; reduce
this to talk about the general approach:

a) annotation of events

b) investigation of model quality,

c) cross-analysis of datasets

d) Possibly cite https://psyarxiv.com/sdbqv/ and declare that this study is
a concrete realization of that promise}

\todo[inline]{Präteritum oder Präsens? Ist momentan gemischt; find's ok so}

\todo[inline]{Inner join of AV \& AO: N=14}

% What we did: Einleitung
In this study, we analyze data of three publicly available datasets from the
same set of 14 participants as part of the studyforrest data set
(\href{http://www.studyforrest.org}{studyforrest.org}). We exploratorily
investigate how the parahippocampal gyrus [or more general ``human brain''?]
responds to ``spatially relevant'' events embedded in a 2h audio-visual movie
\citep{hanke2016simultaneous} and its audio-description (i.e. the audio-only
variant) of the same length \citep{hanke2014audiomovie}. We compare these
results to PPA localizations that were obtained from a dedicated visual
localizer experiment \citep{sengupta2016extension}.

Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
We annotated events in the otherwise unknown temporal structure of both stimuli.
In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
Our rationale was that cuts re-orient the viewer in the depicted environment
indepenten from the exact visual content in the movie frame following the cut.
In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.

In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
\todo[inline]{in order to\dots}

Encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like stimulus free from any task to localize a ``visual area'' in individual study participants.

@@

\section{Methods}

\todo[inline]{Specific data outputs should be explicitly referenced via data
citation (see Data Records and Data Citations, below)}

We used data from three publicly available datsets as part of the studyforrest
dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already
been used by other research groups for independent research questions before.

We used fMRI data from 14 subjects who took part in three different studies. Namely, the same subjects were

a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding}.
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}, a dataset already used by
\citep{ben2018hippocampal}. c) participating in a dedicated block-wise visual
localizer (LOC study) \citep{sengupta2016extension}, a dataset aready used by
\citep{jiahui2019predicting}.

An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications  \citep{hanke2014audiomovie, hanke2016simultaneous,
sengupta2016extension}. Following is a brief summary of most important aspects.

\todo[inline]{Alles um Sengupta ergänzen}

\subsection{Participants}

\todo[inline]{inner join von AO \& AV: N=14; AO: N=19; es fehlt in beiden VP10;
Angaben zu Alter (Durchschnitt; ggf. Range) und Geschlecht sind folglich falsch}

In the AO study, 19 participants (all right-handed, age 21–38 years, mean age
26.6 years, 12 male) listened to the German audio-description
\citep{ForrestGumpGermanAD} of the movie ``Forrest Gump''
\citep{ForrestGumpMovie} as an additional audio track for visually impaired
listeners on Swiss public television. In the AV study, the same 14 participants
(21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track \citep{ForrestGumpDVD}. All participants reported to have normal hearing, normal or corrected-to-normal vision, and no known history of neurological disorders.

\todo[inline]{Sengupta (2016)}
In the LOC study\dots

In both studies, participants received monetary compensation and gave written informed consent for their participation and for public sharing of all obtained data in anonymized form. The studies had prior approval by the Ethics Committee of Otto-von-Guericke University of Magdeburg, Germany.

\subsection{Stimuli}
% stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of
the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
temporally aligned audio-description (i.e. the audio-only variant of the movie)
that was broadcast as an additional audio track for visually impaired listeners
on Swiss public televinsion \citep{ForrestGumpGermanAD}.

% difference in audio track AV vs. AO
The plot of the movie is already carried by an off-screen voice of the main
character Forrest Gump.  In the largely identical audio-description, a male
narrator additionally describes essential aspects of the visual scenery when
there is no off-screen voice, dialog, or other relevant auditory content.

% stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$2h
\citep{hanke2014audiomovie, hanke2016simultaneous}. Both stimuli were further
processed (filtering, volume adjustments) to improve audibility during MRI
scanning. Finally, each stimulus was split into eight segments of approximately
15 minutes.  Except for the first movie segment, each segment started with a
snippet of at least six seconds immediately preceding the movie scene boundary
used to split the segments (s. Figure 3a in \citep{hanke2014audiomovie}.

\todo[inline]{Sengupta (2016)}

\subsection{Naturalistic stimuli annotation}

\todo[inline]{aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen \& anpassen, um Statistiken und runcommand-file zu erstellen}

% annotation procedure
We extended a publicly available annotation of speech \citep{haeusler2020speechanno} by manually annotating the audio-description's narrator: Two persons performed a categorization of nouns embedded in sentences spoken by the narrator to describe the movie's missing visual content.

\todo[inline]{WARUM WAS WIE annotiert wurde; warum Kategorien so gewählt?}

% noun categorization
% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
The nouns were categorized by the clue they provide about the cinematographic
scene's environment (geo, geo-room; setting\_new, setting\_old), its inherent
persons (female, female name; male, male name, person), a person's appearance
(face, head; body, bodypart), and a scene's inherent objects (object,
furniture). See Table \ref{tab:descr-nouns} for a complete overview of all
cateogries [+++rules, counts, examples].

@@

% Tabelle der Descriptive Nouns;
\todo[inline]{decr-stats-anno.py; Schrägstriche vor Platzhalter}

\todo[inline]{Caption hübsch machen}

@@

    \caption{Narrator's descriptive nouns.
        All categories sorted alphapetically.
    Examples are given in English.}

@@

\subsection{Procedure}

In both [all three] studies, participants filled out a questionnaire on their
basic demographic information and familiarity with the audio-description or the
movie. Participants were instructed to inhibit physical movements except for
eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
movie'' respectively. Audio-description and movie segments were presented in
chronological order with four segments in two fMRI sessions respectively.
Between sessions, participants left the scanner for a break with a flexible
duration. Structural images were obtained during the first study on a day
different from the fMRI session.

\subsection{Stimulation setup}

\todo[inline]{irrelevantes kürzen}
In both studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.

In the AO study, visual instructions were presented on a rear-projection screen
inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue. [The screen contained a solid black ``fixation'' dot that faded in and
out at the beginning and end of a movie segment.]

In the AV study, visual instructions and stimuli were presented on a
rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with
EXT-DVI-FM1000)]. The movie was shown at a viewing distance of \unit[63]{cm} in
\unit[720]{p} resolution at full width on a \unit[1280 $\times$ 1024]{pixel}
screen with \unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5
$\times$ 21.2]{cm}, corresponding to \unit[23.75 $\times$ 13.5] or \unit[23.75
$times$ 10.25]{cm} when considering only the movie content and excluding the
horizontal gray bars.

@@
